Electronic polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2019-12-22 paper.tex
modify the SI file
resolve issues with paper and SI

To solve the problem described above, we need to find the
$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
related to both electrostatic and optical properties of a 2D
material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
with $L$, we obtain the sheet polarization density, that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, along the
direction $p$. Following the discussion in the previous section,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of the
lattice size when $L$ is large enough, due to the short decay of the 
induced charge density $\Delta \rho$ into the vacuum (see
Supplementary Figure \ref{SI-fig:rho-profile}).
%
Similar to the molecular polarizability\cite{Israelachvili_2011}, we
utilize the concept of electronic polarizability
$\alpha_{\mathrm{2D}}$, 
which has been used previously to solve
exciton-related problems in 2D materials
\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. 
%
$\alpha_{\mathrm{2D}}$ is a macroscopic quantity that characterizes
the ability to induce dipole moments in a 2D material, and is
associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
\alpha_{\mathrm{2D}}^{pq} \boldsymbol{\overline{E}}_{\mathrm{loc}}^{q}$\cite{T_bik_2004}, where
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is the cell-averaged
``local'' electric field acting on the 2D material to induce
polarization\cite{Wiser_1963}.
% 
Alike to $\mu_{\mathrm{2D}}$,
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is also a macroscopic
quantity that excludes the fields generated by the dipoles of the 2D
sheet from $\boldsymbol{E}$. Note the term ``local'' in
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is adapted to resemble the
Lorentz model\cite{Wiser_1963} which has also been used for other
low-dimensional materials (e.g. nanotube\cite{Benedict_1995} and
molecules\cite{T_bik_2004}, and should be distinguished with the
microscopic local field $\boldsymbol{E}_{\mathrm{loc}}(\boldsymbol{r})$ which is spatially
changing.
%

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. 
    %%
    \textbf{a,} The structures of
  the 2D materials investigated in this 
  study. 
  %%
  \textbf{b,} $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. 
  %%
  \textbf{c,} $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. 
  %%
  \textbf{d,} $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with a slope very
  close to $1$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using different databank from 
  from Ref.~\citenum{Haastrup_2018} (squares),
  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
  \textbf{c} and \textbf{d}. Data corresponding to 2H-MX$_2$ 
  (M=Mo, W; X=O, S, Se, Te) is highlighted in {\bf d}. The very tiny 
  difference in $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$
  between compounds with different metal atoms 
  gives superposed magnitudes not distinguishable in the plot. 
  }
\end{figure}
%
%
computationally and experimentally determined. Despite the
simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
they generate direct relationships between the electronic polarizability and
the electronic/structural properties for any 2D material in a new
framework.

@@

Simulations were carried out using plane-wave density functional
theory package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2}
using the projector augmented wave (PAW) approach with GW
pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA~is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material. This
guarantees that absolute energies were converged to a few meV and the
stress tensor to within 0.01 kBar.  Calculation of the macroscopic
ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA.  Local field effect corrections are included at the
exchange-correlation potential $V_{\mathrm{xc}}$ at both PBE and HSE06
levels. The materials from Ref.\citenum{Haastrup_2018} for comparison
were choses with the GW bandgap larger than 0.05 eV. Bulk layered
materials were constructed by relaxing the c-axis length of
corresponding monolayer material with the interlayer van der Waals
(vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of
Ref.~\citenum{Haastrup_2018} are calculated at PBE level with a
k-point density of 10~\AA$^{-1}$. Local field effect corrections are
also used for the dielectric properties of bulk systems.

>>>>

To solve the problem described above, we need to find the
$L$-independent alternative of $\varepsilon_{\mathrm{SL}}$, which is
related to both electrostatic and optical properties of a 2D
material~\cite{Matthes_2016}. By multiplying Eq.~\ref{eq:def-eps-2}
with $L$, we obtain the sheet polarization density, that is,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} =\boldsymbol{u}^{p}/A$, along the
direction $p$. Following the discussion in the previous section,
$\boldsymbol{\mu}_{\mathrm{2D}}^{p}$ becomes independent of the
lattice size when $L$ is large enough, due to the short decay of the 
induced charge density $\Delta \rho$ into the vacuum (see
Supplementary Figure \ref{SI-fig:rho-profile}).
%
Similar to the molecular polarizability\cite{Israelachvili_2011}, we
utilize the concept of electronic polarizability
$\alpha_{\mathrm{2D}}$, 
which has been used previously to solve
exciton-related problems in 2D materials
\cite{Cudazzo_2011_screening_2D,Olsen_2016_hydrogen,Jiang_2017_Eg_Eb}. 
%
$\alpha_{\mathrm{2D}}$ is a macroscopic quantity that characterizes
the ability to induce dipole moments in a 2D material, and is
associated with $\boldsymbol{\mu}_{\mathrm{2D}}$ through:
$\boldsymbol{\mu}_{\mathrm{2D}}^{p} = \sum_{q}
\alpha_{\mathrm{2D}}^{pq} \boldsymbol{\overline{E}}_{\mathrm{loc}}^{q}$\cite{T_bik_2004}, where
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is the cell-averaged
``local'' electric field acting on the 2D material to induce
polarization\cite{}.
% 
Alike to $\mu_{\mathrm{2D}}$,
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is also a macroscopic
quantity that excludes the fields generated by the dipoles of the 2D
sheet from $\boldsymbol{E}$. Note the term ``local'' in
$\boldsymbol{\overline{E}}_{\mathrm{loc}}$ is adapted to resemble the
Lorentz model\cite{Wiser_1963} which has also been used for other
low-dimensional materials (e.g. nanotube\cite{Benedict_1995} and
molecules\cite{T_bik_2004}, and should be distinguished with the
microscopic local field $\boldsymbol{E}_{\mathrm{loc}}(\boldsymbol{r})$ which is spatially
changing.
%

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.7\linewidth]{img/fig2-with-MX2.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D materials}. 
    %%
    \textbf{a,} The structures of
  the 2D materials investigated in this 
  study. 
  %%
  \textbf{b,} $\alpha_{\mathrm{2D}}^{\parallel}$,
  $\alpha_{\mathrm{2D}}^{\perp}$ (bar plots) and $E_{\mathrm{g}}$
  (blue dots) for all the 2D materials studied.
  $\alpha_{\mathrm{2D}}^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha_{\mathrm{2D}}^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. HSE06 functional is used to obtain the data. 
  %%
  \textbf{c,} $(4\pi \varepsilon_{0})/\alpha_{\mathrm{2D}}^{\parallel}$ (in
  \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the background. 
  %%
  \textbf{d,} $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$ (in \AA{}) as a
  function of $\delta_{\mathrm{cov}}$ (definition schematically shown
  in the inset), showing a perfect linear relation with a slope very
  close to $1$ (i.e.
  $\alpha_{\mathrm{2D}}^{\perp} \approx \varepsilon_{0}
  \delta_{\mathrm{cov}}$ ). The universal scaling relation is also
  revealed using different databank from 
  from Ref.~\citenum{Haastrup_2018} (squares),
  and Ref.~\citenum{Mounet_2018} (triangles) as superimposed on
  \textbf{c} and \textbf{d}. Data corresponding to 2H-MX$_2$ 
  (M=Mo, W; X=O, S, Se, Te) is highlighted in {\bf d}. The very tiny 
  difference in $\alpha_{\mathrm{2D}}^{\perp}/(\varepsilon_{0})$
  between compounds with different metal atoms 
  gives superposed magnitudes not distinguishable in the plot. 
  }
\end{figure}
%
%
computationally and experimentally determined. Despite the
simplicity of Eqs. \ref{eq:2D-Moss-para} and \ref{eq:2D-Moss-perp},
they generate direct relationships between the electronic polarizability and
the electronic/structural properties for any 2D material in a new
framework.

@@

Simulations were carried out using plane-wave density functional
theory package VASP \cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2}
using the projector augmented wave (PAW) approach with GW
pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with spin orbit coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA~is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof99,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material. This
guarantees that absolute energies were converged to a few meV and the
stress tensor to within 0.01 kBar.  Calculation of the macroscopic
ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA.  Local field effect corrections are included at the
exchange-correlation potential $V_{\mathrm{xc}}$ at both PBE and HSE06
levels. The materials from Ref.\citenum{Haastrup_2018} for comparison
were choses with the GW bandgap larger than 0.05 eV. Bulk layered
materials were constructed by relaxing the c-axis length of
corresponding monolayer material with the interlayer van der Waals
(vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of
Ref.~\citenum{Haastrup_2018} are calculated at PBE level with a
k-point density of 10~\AA$^{-1}$. Local field effect corrections are
also used for the dielectric properties of bulk systems.
